Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-08-29 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

%\PeterNote{Should we keep the list of questions in this extensive form?}
%\YuhanNote{I moved it to introduction}

@@

The optimal approximation  based on $n$ series coefficients of the input function is defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
\begin{equation} \label{DHKM:APP_def}
    \APP : \calF \times \N_0 \to \calG, \quad  \APP(f,0) = 0, \ \ \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
\end{equation}
By the argument leading to \eqref{DHKM:SOL_A} it follows that 
\begin{equation} \label{DHKM:APP_Err_Coef}
    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
\end{equation}
An upper bound on the approximation error follows from Lemma \ref{DHKM:Key_Lem}:
\begin{equation} \label{DHKM:Refined_APP_err}
    \norm[\calG]{\SOL(f) - \APP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
    \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
\end{equation}
This leads to the following theorem.

\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.  The error of the approximation defined in \eqref{DHKM:APP_def} is bounded tightly above as 
\begin{equation} \label{DHKM:APP_errorBd}
    \sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}  \le R \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
\end{equation}
Moreover, the worst case error over $\calB_R$ of $\APP'(\cdot,n)$, for any approximation based on $n$ series coefficients of the input function, can be no smaller.
\end{theorem}

@@

    \State Choose $n^* =  \min \left \{n \in \N_0 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \le \varepsilon /R \right \}$

    \RETURN $\ALG(f,\varepsilon) = \APP(f,n^*)$
\end{algorithmic}
\end{algorithm}
We now show that this algorithm is optimal if the input set is a ball.
\begin{theorem}\label{DHKM:thm_cost_non_adapt}
The non-adaptive Algorithm \ref{DHKM:BallAlg} has an information cost for the set of input functions $\calC = \calB_R$ that is given by
\[
\COST(\ALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \le \varepsilon /R \right \}.
\]
This algorithm is essentially optimal for the set of input functions $\calB_R$, namely,
\begin{multline*}
\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calA(\calB_R),\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
\end{multline*}
where $\varepsilon_{\max}$ and $R_{\min}$ are arbitrary and fixed, and $\omega = R_{\min}/R$.
\end{theorem}

@@

\DHKMchange{Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$. It is given by}
\begin{equation} \label{DHKM:pilot_cone}
    \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
\end{equation}
Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.  The definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ allows us to bound these as follows: 
\begin{align*}
     \MoveEqLeft{\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
     & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \qquad \forall f \in \calF \\
    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}.
\end{align*}
This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
\begin{subequations} \label{DHKM:pilot_errbd}
\begin{equation}
\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},
\end{equation}
where 
\begin{multline} \label{ErrNDef}
\ERRN \\
    : =  
    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
    \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
    \\ \forall n \ge n_1.
\end{multline}
\end{subequations}
This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.  This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}:

@@

\begin{theorem} \label{DHKM:PilotCostThm}
Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}.  The information cost is
\begin{multline} \label{DHKM:PilotConeAlg_cost}
    \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R) \\
    = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le \varepsilon/[(A^\rho -1)^{1/\rho}R] \right \}.
\end{multline}
There exist positive $\varepsilon_{\max}$ and $R_{\min}$ for which the computational complexity has the lower bound
\begin{multline} \label{DHKM:PilotConeAlg_comp}
        \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
    \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
\end{multline}
Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ contains only adaptive algorithms.
\end{theorem}

\begin{proof} 
The upper bound on the computational cost of this algorithm is obtained by noting that 
\begin{align*}
    \MoveEqLeft[1]{\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R)} \\
    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
     & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1 }} \, 
     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
    \le \varepsilon \right \} \\   
     & \le \min \left \{n \ge n_1 : 
     (A^\rho -1)^{1/\rho} R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
    \le \varepsilon \right \},  
\end{align*}
since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.  Moreover, this inequality is tight for some $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.  This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.

@@

Using an argument like that in the proof of  Theorem \ref{DHKM:APP_optimality_thm}, it follows that 
\begin{align*}
\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
+ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
=\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
& \ge \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
\end{align*}
by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.  By the choice of $R_{\min}$ and $\varepsilon_{\max}$ above, it follows that $n > n_1$.  This inequality then implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}. Because $\lim_{R \to \infty} \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ contains only adaptive algorithms.

@@

\begin{lemma}\label{DHKM:lambdineq}
Consider the ordered weights,
$\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$
then we have
\[ 
\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \qquad \forall p >0,
\]
provided that $\norm[p]{\bslambda}$ is finite.
\end{lemma}
\begin{proof}
Since the $\lambda_{\bsk_i}$ are non-increasing it follows that 
\begin{equation*}
    n \lambda_{\bsk_{n+1}}^p \le 
    \lambda_{\bsk_{1}}^p + \lambda_{\bsk_{2}}^p + \cdots 
    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \bbK}^\infty \lambda_{\bsk}^p = \norm[p]{\bslambda}^p \qquad \forall p > 0.
\end{equation*}
Dividing both sides by $n$ and taking the $p^{\text{th}}$ root completes the proof.
\end{proof}

@@

\begin{lemma}\label{DHKM:prodwtsupperbound}
For $\bslambda = \bigl(\lambda_{\bsk} \bigr)_{\bsk \in \bbN_0^d}$ defined in \eqref{DHKM:prodwts}
we have 
\begin{align*}
\norm[p]{\bslambda} &\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
 \norm[p]{\bslambda} & \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1,
\end{align*}
where $\zeta$ is the Riemann zeta function.
\end{lemma}
\begin{proof}
The proof proceeds by straightforward calculation under the assumption that $\norm[p]{\bss}$ is finite:
\begin{align*}
   \norm[p]{\bslambda}^ p & 
   = \sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p  
   = \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) 
   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right) 
   \qquad \text{ by \eqref{DHKM:prodwts} }\\
    & = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\norm[p]{\bss}^p \bigr) \right)\\
 &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p} \norm[p]{\bss}^p \right) = \exp\left(\norm[p]{\bsw}^p\norm[p]{\bss}^p \right)
\quad \text{since }\log(1+x) \le x \ \forall x\ge 0.
\end{align*}
Taking the $p^{\text{th}}$ root completes the proof for the general case.  For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\norm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
\end{proof}

@@

Lemmas \ref{DHKM:lambdineq} and \ref{DHKM:prodwtsupperbound} imply upper bounds on $\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} = \lambda_{\bsk_{n+1}}$:
\begin{align*}
\lambda_{\bsk_{n+1}} &\le \frac{1}{n^{1/p}} \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
\lambda_{\bsk_{n+1}} & \le \frac{1}{n^{1/p}} \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \  \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1.
\end{align*}
These upper bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} imply upper bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp} for all $p > 1/r$:
\begin{equation*}
    \text{Algorithm \ref{DHKM:BallAlg}:} \quad \COST(\ALG,\calB_R,\varepsilon, R') 
    \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil,
    \end{equation*}
    \begin{multline*}
    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
    \\ \le \max \left( n_1, 
    \left \lceil  \left(\frac{AR}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil \right).
    \end{multline*}
Note that these costs are $\calO(R^p \varepsilon^{-p})$ for all $p > 1/r$. A faster decay rate of the $\lambda_{\bsk}$ due to the faster decay rate of the smoothness coefficients, $s_k$, implies asymptotically smaller information cost.
}

@@

\FredNote{I think that we need a lower bound on $\lambda_{\bsk_{n+1}}$ to obatain lower bounds on the computational complexity. }

>>>>

@@

The optimal approximation  based on $n$ series coefficients of the input function is defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
\begin{equation} \label{DHKM:APP_def}
    \APP : \calF \times \N_0 \to \calG, \quad  \APP(f,0) = 0, \ \ \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
\end{equation}
By the argument leading to \eqref{DHKM:SOL_A} it follows that 
\begin{equation} \label{DHKM:APP_Err_Coef}
    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
\end{equation}
An upper bound on the approximation error follows from Lemma \ref{DHKM:Key_Lem}:
\begin{gather} \label{DHKM:Refined_APP_err}
    \norm[\calG]{\SOL(f) - \APP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
    \bignorm[\rho']{\bslambda^{(n+1)}}, \\
    \intertext{where the tail of $\bslambda$ is defined by}
    \label{DHKM:taillambds}
     \bslambda^{(n)} : = \bigl(  \lambda_{\bsk_i}  \bigr)_{i = n}^{\infty}.
\end{gather}
This leads to the following theorem.

\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.  The error of the approximation defined in \eqref{DHKM:APP_def} is bounded tightly above as 
\begin{equation} \label{DHKM:APP_errorBd}
    \sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}  \le R \, \bignorm[\rho']{\bslambda^{(n+1)}}.
\end{equation}
Moreover, the worst case error over $\calB_R$ of $\APP'(\cdot,n)$, for any approximation based on $n$ series coefficients of the input function, can be no smaller.
\end{theorem}

@@

    \State Choose $n^* =  \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}$

    \RETURN $\ALG(f,\varepsilon) = \APP(f,n^*)$
\end{algorithmic}
\end{algorithm}
We now show that this algorithm is optimal if the input set is a ball.
\begin{theorem}\label{DHKM:thm_cost_non_adapt}
The non-adaptive Algorithm \ref{DHKM:BallAlg} has an information cost for the set of input functions $\calC = \calB_R$ that is given by
\[
\COST(\ALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}.
\]
This algorithm is essentially optimal for the set of input functions $\calB_R$, namely,
\begin{multline*}
\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calA(\calB_R),\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
\end{multline*}
where $\varepsilon_{\max}$ and $R_{\min}$ are arbitrary and fixed, and $\omega = R_{\min}/R$.
\end{theorem}

@@

\DHKMchange{Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$. It is given by}
\begin{equation} \label{DHKM:pilot_cone}
    \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
\end{equation}
Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.  The definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ allows us to bound these as follows: 
\begin{align*}
     \MoveEqLeft{\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
     & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \qquad \forall f \in \calF \\
    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
    \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}.
\end{align*}
This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
\begin{subequations} \label{DHKM:pilot_errbd}
\begin{equation}
\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},
\end{equation}
where 
\begin{multline} \label{ErrNDef}
\ERRN \\
    : =  
    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
    \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} , 
    \\ \forall n \ge n_1.
\end{multline}
\end{subequations}
This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.  This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}:

@@

\begin{theorem} \label{DHKM:PilotCostThm}
Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}.  The information cost is
\begin{multline} \label{DHKM:PilotConeAlg_cost}
    \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R) \\
    = \min \left \{n \ge n_1 : \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} \,
    \le \varepsilon/[(A^\rho -1)^{1/\rho}R] \right \}.
\end{multline}
There exist positive $\varepsilon_{\max}$ and $R_{\min}$ for which the computational complexity has the lower bound
\begin{multline} \label{DHKM:PilotConeAlg_comp}
        \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}),\varepsilon,R) \ge \min \left \{n \ge n_1 : \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} \,
    \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
    \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
\end{multline}
Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ contains only adaptive algorithms.
\end{theorem}

\begin{proof} 
The upper bound on the computational cost of this algorithm is obtained by noting that 
\begin{align*}
    \MoveEqLeft[1]{\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R)} \\
    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
     & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1 }} \, 
     \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}}
    \le \varepsilon \right \} \\   
     & \le \min \left \{n \ge n_1 : 
     (A^\rho -1)^{1/\rho} R \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}}
    \le \varepsilon \right \},  
\end{align*}
since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.  Moreover, this inequality is tight for some $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.  This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.

@@

Using an argument like that in the proof of  Theorem \ref{DHKM:APP_optimality_thm}, it follows that 
\begin{align*}
\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
+ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
=\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
& \ge \frac{R(1 - 1/A)}{2} \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} ,
\end{align*}
by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.  By the choice of $R_{\min}$ and $\varepsilon_{\max}$ above, it follows that $n > n_1$.  This inequality then implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}. Because $\lim_{R \to \infty} \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ contains only adaptive algorithms.

@@

\begin{lemma}\label{DHKM:lambdineq}
Consider the ordered weights,
$\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$
then we have
\[ 
\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \quad \forall p >0, 
\qquad \sup_{n \in \bbN} \lambda_{\bsk_{n}} n^{\eta/p} \ge \frac{\norm[p]{\bslambda}}{\zeta(\eta)^{1/p}} \quad \forall \eta > 1, \ p>0.
\]
\end{lemma}
\begin{proof}
Since the $\lambda_{\bsk_i}$ are non-increasing it follows that 
\begin{equation*}
    n \lambda_{\bsk_{n+1}}^p \le 
    \lambda_{\bsk_{1}}^p + \lambda_{\bsk_{2}}^p + \cdots 
    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \bbK} \lambda_{\bsk}^p = \norm[p]{\bslambda}^p \qquad \forall p > 0.
\end{equation*}
Dividing both sides by $n$ and taking the $p^{\text{th}}$ root completes the proof.
\end{proof}

@@

\begin{lemma}\label{DHKM:prodwtsupperbound}
For $\bslambda = \bigl(\lambda_{\bsk} \bigr)_{\bsk \in \bbN_0^d}$ defined in \eqref{DHKM:prodwts}
we have 
\begin{align*}
\norm[p]{\bslambda} &\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
 \norm[p]{\bslambda} & \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1,
\end{align*}
where $\zeta$ is the Riemann zeta function.
\end{lemma}
\begin{proof}
The proof proceeds by straightforward calculation under the assumption that $\norm[p]{\bss}$ is finite:
\begin{align*}
   \norm[p]{\bslambda}^ p & 
   = \sum_{\bsk \in \NN_0^d} \lambda_{\bsk}^p  
   = \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) 
   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right) 
   \qquad \text{ by \eqref{DHKM:prodwts} }\\
    & = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\norm[p]{\bss}^p \bigr) \right)\\
 &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p} \norm[p]{\bss}^p \right) = \exp\left(\norm[p]{\bsw}^p\norm[p]{\bss}^p \right)
\quad \text{since }\log(1+x) \le x \ \forall x\ge 0.
\end{align*}
Taking the $p^{\text{th}}$ root completes the proof for the general case.  For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\norm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
\end{proof}

@@

Lemmas \ref{DHKM:lambdineq} and \ref{DHKM:prodwtsupperbound} imply upper bounds on $\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} = \lambda_{\bsk_{n+1}}$:
\begin{align*}
\lambda_{\bsk_{n+1}} &\le \frac{1}{n^{1/p}} \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
\lambda_{\bsk_{n+1}} & \le \frac{1}{n^{1/p}} \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \  \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1.
\end{align*}
These upper bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} imply upper bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp} for all $p > 1/r$:
\begin{align*}
    \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \COST(\ALG,\calB_R,\varepsilon, R') 
    \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil, \\
    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
    \\ & \qquad \qquad \le \max \left( n_1, 
    \left \lceil  \left(\frac{AR}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil \right).
    \end{align*}
Note that these costs are $\calO(R^p \varepsilon^{-p})$ for all $p > 1/r$. A faster decay rate of the $\lambda_{\bsk}$ due to the faster decay rate of the smoothness coefficients, $s_k$, implies asymptotically smaller information cost.
}

@@

\FredNote{I think that we need a lower bound on $\lambda_{\bsk_{n+1}}$ to obtain lower bounds on the computational complexity. }
